---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# psfmi

[![CRAN_Release_Badge](https://www.r-pkg.org/badges/version-ago/psfmi)](https://CRAN.R-project.org/package=psfmi)
[![Monthly downloads badge](https://cranlogs.r-pkg.org/badges/last-month/psfmi?color=blue)](https://CRAN.R-project.org/package=psfmi)
[![Travis Build Status](https://travis-ci.com/mwheymans/psfmi.svg?branch=master)](https://travis-ci.org/mwheymans/psfmi) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.6.0-6666ff.svg)](https://cran.r-project.org/)

The package provides functions to apply pooling, backward and forward selection 
of logistic and Cox regression prediction models in multiply imputed data sets 
using Rubin's Rules (RR), the D1, D2, D3 and the median p-values method. 
The model can contain	continuous, dichotomous, categorical and restricted cubic 
spline predictors and interaction terms between all these type of predictors. 

Validation of the prediction models can be performed with cross-validation or bootstrapping 
in multiply imputed data sets and pooled model performance measures as AUC value, 
R-square, scaled Brier score and calibration plots are generated. Also a function 
to externally validate logistic	prediction models in multiple imputed data sets
is available.

## Installation

You can install the released version of psfmi with:

``` r
install.packages("psfmi")
```
And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mwheymans/psfmi")
```

## Example

This example shows you how to apply forward selection with a model that includes a 
restricted cubic spline function and an interaction term.

```{r example}
library(psfmi)

pool_lr <- psfmi_lr(data=lbpmilr, formula = Chronic ~ rcs(Pain, 3) + JobDemands + rcs(Tampascale, 3) +
                   factor(Satisfaction) + Smoking + factor(Satisfaction)*rcs(Pain, 3) ,
                   p.crit = 0.05, direction="FW", nimp=5, impvar="Impnr",
                   method="D1")
pool_lr$RR_model_final

```

