---
title: "Welcome to the psfmi package"
author: "Martijn W Heymans"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{psfmi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

On this page you will find information of the psfmi package. 
The	package contains functions to apply pooling or backward 
selection (BWS) for logistic, Cox regression and Multilevel
(Mixed models) prediction models in multiply imputed datasets. 

The basic pooling method is Rubin's Rules. For categorical predictors, 
different methods to derive pooled p-values are available as: 
the D1, D2, D3 and MPR (Median R Rule) method. Also restricted 
cubic spline coefficients can be used. Two-way interaction terms 
between continuous, dichotomous and categorical predictors are also 
possible in the model. All these type of predictors, interaction terms 
or a combination, can be forced in the model during BWS. 
Furthermore, the stability of models selected and the bootstrap inclusion 
frequency can be evaluated. For logistic and Cox regression models bootstrapping 
is than used and for Multilevel models cluster bootstrapping.

The package also contains functions to generate	apparent model performance 
measures over imputed datasets as ROC/AUC, Nagelkerke R-squares, 
Hosmer & Lemeshow test values and calibration plots. A wrapper function 
over Frank Harrell's validate function is available. Bootstrap internal 
validation is performed in each imputed dataset and results are pooled. 
BWS as part of internal validation is optional and recommended.
A function with the name mivalext_lr can be used to externally validate
prediction models in multiple imputed datasets. The following information 
of the externally validated model is provided: pooled ROC/AUC, (Nagelkerke) 
R-Square value, Hosmer and Lemeshow Test, pooled coefficients when the model 
is freely estimated in imputed datasets and the pooled linear predictor (LP), 
with information about miscalibration in intercept and slope. 

## Installing the psfmi package

The package can be installed from CRAN and the development version from Github 
by running the following code in the R console window:
 
 install.packages("devtools")
 
 library(devtools)
 
 devtools::install_github("mwheymans/psfmi")
 
 library(psfmi)

## Main functions

The main functions that are available in the psfmi package are:

psfmi_lr: pooling and selection of Logistic regression models in multiply imputed datasets. 

psfmi_coxr: pooling and selection of Cox regression models in multiply imputed datasets.

psfmi_mm: pooling and selection of linear and logistic Mixed models in multiply imputed datasets.

psfmi_stab: stability evaluation of models and predictors in multiply imputed datasets.

miperform_lr: for performance and internal validation of logistic regression 
models in multiply imputed datasets.

mivalext_lr: external validation in multiply imputed datasets.

## Examples 

* [Logistic Regression]
    + [Pooling without BWS and method D1] 
    + [Pooling with BWS and method D1] 
    + [Pooling with BWS including several interaction terms and method D2]
    + [Pooling with BWS and forcing interaction terms and method D1]
    + [Pooling with BWS including spline coefficient and method D1]
      
* [Cox regression]
    + [Pooling without BWS and method D1] 
    + [Pooling with BWS and method MPR] 
    + [Pooling with BWS including interaction terms and method D2]
    + [Pooling with BWS including spline coefficient and method D1]

## Logistic Regression

### Pooling without BWS and method D1

```{r}

  library(psfmi)
  pool_lr <- psfmi_lr(data=lbpmilr, nimp=5, impvar="Impnr", Outcome="Chronic",
  predictors=c("Gender", "Smoking", "Function", "JobControl",
  "JobDemands", "SocialSupport"), method="D1")
  pool_lr$RR_Model
  pool_lr$multiparm
  
```

Back to [Examples]

### Pooling with BWS and method D1

Pooling Logistic regression models over 5 imputed datasets with backward selection
using a p-value of 0.05 and as method D1 and forcing the predictor "Smoking" in the 
models during backward selection.

```{r}

  library(psfmi)
  pool_lr <- psfmi_lr(data=lbpmilr, nimp=5, impvar="Impnr", Outcome="Chronic",
  predictors=c("Gender", "Smoking", "Function", "JobControl",
  "JobDemands", "SocialSupport"), keep.predictors = "Smoking",
  p.crit = 0.05, method="D1")
  pool_lr$RR_Model
  pool_lr$multiparm
  pool_lr$predictors_in
  
```

Back to [Examples]

### Pooling with BWS including several interaction terms and method D2
      
Pooling Logistic regression models over 5 imputed datasets with BWS
using a p-value of 0.05 and as method D2. Several interaction terms,
including a categorical predictor, are part of the selection procedure.

```{r}

  library(psfmi)
  pool_lr <- psfmi_lr(data=lbpmilr, nimp=5, impvar="Impnr", Outcome="Chronic",
  predictors=c("Gender", "Smoking", "Function", "JobControl"), 
  p.crit = 0.05, cat.predictors = c("Carrying", "Satisfaction"),
  int.predictors = c("Carrying:Smoking", "Gender:Smoking"), method="D2")
  pool_lr$RR_Model
  pool_lr$multiparm
  pool_lr$predictors_in
  
```

Back to [Examples]

### Pooling with BWS and forcing interaction terms and method D1
      
Same as above but now forcing several predictors, including interaction terms,
in the model during BWS.

```{r}

  library(psfmi)
  pool_lr <- psfmi_lr(data=lbpmilr, nimp=5, impvar="Impnr", Outcome="Chronic",
  predictors=c("Gender", "Smoking", "Function", "JobControl"), 
  p.crit = 0.05, cat.predictors = c("Carrying", "Satisfaction"),
  int.predictors = c("Carrying:Smoking", "Gender:Smoking"),
  keep.predictors = c("Smoking:Carrying", "JobControl"), method="D1")
  pool_lr$RR_Model
  pool_lr$multiparm
  pool_lr$predictors_in
  
```

Back to [Examples]

### Pooling with BWS including spline coefficient and method D1

Pooling Logistic regression models over 5 imputed datasets with BWS
using a p-value of 0.05 and as method D1. A spline predictor and interaction 
term are part of the selection procedure.

```{r}

  library(psfmi)
  pool_lr <- psfmi_lr(data=lbpmilr, nimp=5, impvar="Impnr", Outcome="Chronic",
  predictors=c("Gender", "Smoking", "JobControl"), 
  p.crit = 0.05, cat.predictors = c("Carrying", "Satisfaction"),
  spline.predictors=c("Function"), int.predictors = c("Carrying:Smoking"), 
  knots=3, method="D1")
  pool_lr$RR_Model
  pool_lr$multiparm
  pool_lr$predictors_in

```

Back to [Examples]

## Cox Regression

### Pooling without BWS and method D1

```{r}

  library(psfmi)
  pool_coxr <- psfmi_coxr(data=lbpmicox, nimp=5, impvar="Impnr", time="Time", status="Status",
  predictors=c("Duration", "Radiation", "Onset", "Function", "Age",
  "Previous", "Tampascale", "JobControl", "JobDemand", "Social"), p.crit=1,
  cat.predictors=c("Expect_cat"), method="D1")
  pool_coxr$RR_Model
  pool_coxr$multiparm
  
```  

Back to [Examples]

### Pooling with BWS and method MPR

```{r}

  library(psfmi)
  pool_coxr <- psfmi_coxr(data=lbpmicox, nimp=5, impvar="Impnr", time="Time", status="Status",
  predictors=c("Duration", "Radiation", "Onset", "Function", "Age",
  "Previous", "Tampascale"), p.crit=0.05,
  cat.predictors=c("Expect_cat"), method="MPR")
  pool_coxr$RR_Model
  pool_coxr$multiparm
  pool_coxr$predictors_in
  
```  

Back to [Examples]

### Pooling with BWS including interaction terms and method D2

Pooling Cox regression models over 5 imputed datasets with backward selection
using a p-value of 0.05 and as method D2 including interaction terms with 
a categorical predictor and forcing the predictor Tampascale in the models 
during backward selection.

```{r}

  library(psfmi)
  pool_coxr <- psfmi_coxr(data=lbpmicox, nimp=5, impvar="Impnr", time="Time", status="Status",
  predictors=c("Duration", "Previous",  "Radiation", "Onset",
  "Function", "Tampascale" ), p.crit=0.05, cat.predictors=c("Satisfaction",
  "Expect_cat"), int.predictors=c("Tampascale:Radiation",
  "Expect_cat:Tampascale"), keep.predictors = "Tampascale", method="D2" )
  pool_coxr$RR_Model
  pool_coxr$multiparm
  pool_coxr$predictors_in
  
```  

Back to [Examples]

### Pooling with BWS including spline coefficients and method D1

Pooling Cox regression models over 5 imputed datasets with backward selection
using a p-value of 0.05 and as method D1 including a restricted cubic spline 
predictor and forcing Tampascale in the models during backward selection.

```{r}

  library(psfmi)
  pool_coxr <- psfmi_coxr(data=lbpmicox, nimp=5, impvar="Impnr", time="Time", status="Status",
  predictors=c("Duration", "Previous",  "Radiation", "Onset", "Function"), 
  p.crit=0.05, cat.predictors=c("Satisfaction"), spline.predictors=c("Tampascale"),
  int.predictors=c("Tampascale:Radiation"), keep.predictors = "Tampascale", 
  knots=3, method="D1")
  pool_coxr$RR_Model
  pool_coxr$multiparm
  pool_coxr$predictors_in
  
```  

Back to [Examples]
