---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(psfmi)
```


## Topic 1

### Exercise 1a

Write the code to answer question 1a

```{r exercise1a, exercise=TRUE, exercise.eval=TRUE}

pool_lr <- psfmi_lr(data=lbpmilr, nimp=5, impvar="Impnr", Outcome="Chronic",
                    predictors=c("Gender"), p.crit = 1, cat.predictors = NULL, method="D1")
pool_lr$RR_Model

```

```{r exercise1a-hint}

pool_lr <- psfmi_lr(data=lbpmilr, nimp=5, impvar="Impnr", Outcome="Chronic",
                    predictors=c("Gender", "Smoking", "Function", "JobControl", "JobDemands",
                     "SocialSupport"), p.crit = 1, cat.predictors = c("Carrying",  "Satisfaction"), 
                    method="D1", direction = NULL)
pool_lr$RR_Model
pool_lr$multiparm

```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

